Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-15 paper/ijcai/paper.tex
table3 fixed
replacing diagnosis performance table with a chart
fixing issue

\begin{table*}[h]
	\centering
	  \begin{tabular}{l|cccc|cccc|c}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\

@@

Table \ref{tab:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}. $\Delta C <0$ means that the faulty statement may be removed. $\Delta C=0$ means that the faulty statement remained in the same position. $\Delta C >0$ means that \ds{} improved diagnosability.

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$$C$             &  \combpar{5}  & \combpar{10} \\
		\midrule
		$<0$  & 19.53\% & 16.02\% \\
		$=0$  & 46.88\% & 41.80\% \\
		$>0$  & 33.59\% & 42.19\% \\

		\bottomrule
	\end{tabular}
	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
	\label{tab:diagnosis}
\end{table}
\normalsize

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 522.47     & 684.89   & 611.04   \\ \midrule
Median & 50.375      & 66.25               & 54.3                \\ \midrule
Variance & 1191.12      & 1361.83   & 1301.78    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.48 \\ p-value = 1.10 x $10^{-26}$} & \makecell{W = 0.55 \\ p-value = 4.31 x $10^{-25}$} & \makecell{W = 0.52 \\ p-value = 6.23 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 28.97 \\ p-value = 5.13 x $10^{-7}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table*}

>>>>

\begin{table*}[h]
	\small
	% \setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|cccc|cccc|c}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\

@@

Table \ref{fig:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}. $\Delta C <0$ means that the faulty statement may be removed. $\Delta C=0$ means that the faulty statement remained in the same position. $\Delta C >0$ means that \ds{} improved diagnosability.

@@

% \begin{table}[h]
% 	\centering
% 	\setlength{\tabcolsep}{4pt}
% 	\begin{tabular}{ccc}
% 		\toprule
% 		$\Delta$$C$             &  \combpar{5}  & \combpar{10} \\
% 		\midrule
% 		$<0$  & 19.53\% & 16.02\% \\
% 		$=0$  & 46.88\% & 41.80\% \\
% 		$>0$  & 33.59\% & 42.19\% \\
%
% 		\bottomrule
% 	\end{tabular}
% 	\caption {Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
% 	\label{tab:diagnosis}
% \end{table}

\begin{figure}[h]
		\includegraphics[width=0.45\textwidth]{figures/performance.pdf}
		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
		\label{fig:diagnosis}
\end{figure}

\begin{table*}[h]
	\small
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 522.47     & 684.89   & 611.04   \\ \midrule
Median & 50.375      & 66.25               & 54.3                \\ \midrule
Variance & 1191.12      & 1361.83   & 1301.78    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.48 \\ p-value = 1.10 x $10^{-26}$} & \makecell{W = 0.55 \\ p-value = 4.31 x $10^{-25}$} & \makecell{W = 0.52 \\ p-value = 6.23 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 28.97 \\ p-value = 5.13 x $10^{-7}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table*}
